Working title: Verifying the Edmonds-Karp Algorithm

### 2016-02-25 paper/root.tex
More summary for refine-sectioon

    Use efficient data structures:
      Arrays for c,f, and ps
      List for augmenting path. [TODO/Future work: Iterator scheme]

  NetCheck

>>>>

    Use efficient data structures:
      Arrays for c,f, and ps. c and f in row-major indexing.

      List for augmenting path. [TODO/Future work: Iterator scheme]

      In BFS, we use lists for the queues (we have split the queue into one for 
        the current level, and one for the next level), and an array for the predecessor map.

      The refinement is performed using the Sepref tool.

  NetCheck
    We also implemented an algorithm that reads a list of edges and a source and target node, 
    converts it to a capacity matrix and an adjacency map, and checks whether the resulting graph satisfies our network assumptions.
    We proved that this algorithm returns the corresponding Network and adjacency function iff the input describes a valid network,
    and returns a failure value otherwise.

  Combining the implementation of the Edmonds-Karp algorithm with the Network checker yields our final algorithm,
  for which we can export code, and have proved the theorem: [...].
